MSDS 6372 Project 1 Objective 2

### 2020-02-18 Codebooks/MSDS6372.Project.O2.Rmd
Add files via upload

```{r drop irrelevant variables}
#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))
head(nyc2)
```

@@

```{r linearity check}
#nyc4 %>% pairs() No color model
pairs(nyc4,col=nyc4$neighbourhood) #Color by neighborhood
```

@@

```{r linearity check of log-linear model}
pairs(log.nyc,col=log.nyc$neighbourhood)
```

@@

```{r linearity check of log-log model}
pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
```

@@

```{r linearity check of binned independent variables}
nyc.bin.model <-lm(price~.,data=nyc.bins)
#nyc.bins  %>% pairs() No color model
pairs(nyc.bins,col=nyc.bins$neighbourhood) #Color by neighborhood
```

@@

```{r}
plot(nyc4$neighbourhood, nyc4$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check", col=c(7,32,52,82,107)) 
```

- Narrowing down neighborhoods (randomly) to confirm neighbourhood is a significant categorical metrics to keep in MLR

```{r}
nycNeighborhood <- ddply(nyc4,.(neighbourhood), function(x) x[sample(nrow(x),1),])

plot(nycNeighborhood$neighbourhood, nycNeighborhood$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check") 
```

@@

#### Modeling
- We are not seeing any linear correlation between the dependent and independent numeric varaibles
  - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
- We are seeing a strong linear correlation between the dependent and independent categorical variables
- We have surfaced the best residuals assumptions matched in a log-linear model
  - Due to these discoveries we are moving forward with a Two-Way ANOVA in order to create the strongest model
- The number of Neighborhoods is so high deriving any sort of practical significance in a two-way ANOVA would be too difficult. 
  - Changing our selected variables to Neighbourhod_Group and room_type

>>>>

```{r drop irrelevant variables}
#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
nyc2 <- select(nycraw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood"))
head(nyc2)
```

@@

```{r linearity check}
#nyc4 %>% pairs() No color model
pairs(nyc4,col=nyc4$neighbourhood_group) #Color by neighborhood
```

@@

```{r linearity check of log-linear model}
pairs(log.nyc,col=log.nyc$neighbourhood_group)
```

@@

```{r linearity check of log-log model}
pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
```

@@

```{r linearity check of binned independent variables}
nyc.bin.model <-lm(price~.,data=nyc.bins)
#nyc.bins  %>% pairs() No color model
pairs(nyc.bins,col=nyc.bins$neighbourhood_group) #Color by neighborhood
```

@@

```{r}
plot(nyc4$neighbourhood_group, nyc4$price, xlab = "Neighbourhood Group", ylab = "Price", title = "Price v Neighbourhood Group Correlation Check", col=c(7,32,52,82,107)) 
```

```{r}
#Narrowing down neighborhoods (randomly) to confirm neighbourhood is a significant categorical metrics to keep in MLR
#nycNeighborhood <- ddply(nyc4,.(neighbourhood), function(x) x[sample(nrow(x),1),])

#plot(nycNeighborhood$neighbourhood_group, nycNeighborhood$price, xlab = "Neighbourhood", ylab = "Price", title = "Price v Neighbourhood Correlation Check") 
```

@@

#### Modeling
- We are not seeing any linear correlation between the dependent and independent numeric (continuous) varaibles
  - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
- We are seeing a strong linear correlation between the dependent and independent categorical variables
- We have surfaced the best residuals assumptions matched in a log-linear model
  - Due to these discoveries we are moving forward with a Two-Way ANOVA in order to create the strongest model
- The number of Neighborhoods is so high deriving any sort of practical significance in a two-way ANOVA would be too difficult. 
  - Changing our selected variables to Neighbourhod_Group and room_type
